Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 algorithm_regret.tex
fixed upper bound

For the remainder of the proof, we consider phases $s$
with $\EarlyCut{s} \leq \TieCutoff$.
We first consider agents \AgV incurring positive regret less than \EarlyCut{s}.
The second-best arm \Second{\AgV} of such an agent \AgV must satisfy
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \EarlyCut{s}$.
By Assumption~\ref{A1}, and because $\EarlyCut{s} \leq \TieCutoff$,
%Lemma~\ref{lem:sdelta},
the total measure of such agents
is $\AlmostTied{\EarlyCut{s}} \leq \TieDensity \cdot \EarlyCut{s}$,
and each such agent incurs regret at most \EarlyCut{s}.
Summing over all time steps,
and using Lemma~\ref{lem:phase-length} to bound the number of time
steps in phase $s$, 
\pfcomment{We'll have to fix a probability bug here.}
the expected total regret from such agents is at most
\begin{align}
\Expect{\sum_{s=1}^{T} \sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot \EarlyCut[2]{s}}
& \leq \sum_{s=1}^{T} \TieDensity \cdot g^2(s) \ARMNUM \log(s).
\label{equ:small_regret_bound}
\end{align}

We next bound the regret incurred in time steps with large regret.
Let the random variable $t_s$ be the final time step in phase $s$,
for each $s$.
\dkcomment{We have already used $t_s$ before, e.g., in the preceding
  formula. Do we need to redefine it here?}
\pfcomment{Above we define $t_s$ to be the start time of phase $s$.}
\dkcomment{So the new $t_s$ is the old $t_{s+1}-1$? That's a really
  confusing subtle notation change. Is there a way we can avoid this
  and just decide on one or the other, and use it consistently?}
Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
time step in the \Kth{s} phase,
with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
i.e., $k > t_{s}-t_{s-1}$.
By Lemma~\ref{lem:right-choice},
under \AccEU{\tau_s^k}{\frac{\dkedit{\EarlyCut{s}}}{2\Diam d}}, no agent at time $t$ will incur
regret more than \EarlyCut{s}.
\dkcomment{Instead of the extra case distinction, I had thought of
  defining \EarlyCut{s} to be the minimum of the current definition and
  \TieCutoff. Unfortunately, I think that we cannot necessarily apply
  Lemma~\ref{lem:right-choice} with that definition. Just putting that
  here in case you are thinking of simplifying the proof this way.}

>>>>

For the remainder of the proof, we consider phases $s$
with $\EarlyCut{s} \leq \TieCutoff$.
\pfedit{
We first consider agents \AgV incurring positive regret less than \EarlyCut{s}.
Let $A$ be the set of types satisfying 
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \EarlyCut{s}$.
By Assumption~\ref{A1}, and because $\EarlyCut{s} \leq \TieCutoff$,
the total measure of $A$
is $\AlmostTied{\EarlyCut{s}} \leq \TieDensity \cdot \EarlyCut{s}$,
Then, by Lemma~\ref{lem:phase-length},
the expected number of pulls in phase $s$ by agents in $A$  
bounded above by $\TieDensity\ \EarlyCut{s} \ARMNUM \log(s)$, and the total expected number of pulls by these agents by $\sum_{s=1}^T \TieDensity \ \EarlyCut[2]{s} \ARMNUM \log(s)$.
Consider any agent $\AgV$ incurring positive regret less than $\EarlyCut{s}$.
This agent's type must be in $A$.
Moreover, this agent's regret is bounded above by $\EarlyCut{s}$.
Thus, the expected total regret from such agents is at most
\begin{equation}
\sum_{s=1}^{T} \TieDensity \cdot \EarlyCut[2]{s} \ARMNUM \log(s).
\label{equ:small_regret_bound}
\end{equation}
}

We next bound the regret incurred in time steps with large regret.
Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
time step in the \Kth{s} phase,
with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
i.e., $k > \pfedit{t_{s+1}-t_{s}}$.
By Lemma~\ref{lem:right-choice},
under \AccEU{\tau_s^k}{\frac{\dkedit{\EarlyCut{s}}}{2\Diam d}}, no agent at time $t$ will incur
regret more than \EarlyCut{s}.
\dkcomment{Instead of the extra case distinction, I had thought of
  defining \EarlyCut{s} to be the minimum of the current definition and
  \TieCutoff. Unfortunately, I think that we cannot necessarily apply
  Lemma~\ref{lem:right-choice} with that definition. Just putting that
  here in case you are thinking of simplifying the proof this way.}
